### 2013-02-13 doc/xps2013/proposal.tex
fixed bug in bib file & a few bugs in tex file 	modified:   proposal.bib 	modified:   proposal.tex

PI Oskin has traditionally participated in the computer-architecture research
community, co-PI Ceze, in addition to the architecture community also has a
presence in the systems and programming languages community, and co-PI Kahan
has participated mainly in the parallel and scientific computing community.
The move toward multicore architectures has re-invigorated collaboration
across these divides and recent joint work by Oskin, Ceze, and Kahan
embodies this important trend. There are currently five graduate students for
which at last two of the PIs serve as advisors. In addition to the project
described in this proposal, they are also working together on techniques for
detecting concurrency errors with machine learning and language
specifications, using disciplined approximations to save energy in computing,
and developing new operating-system abstractions for emerging non-volatile
memory devices. What has made these collaborations so fruitful in such a short
period of time is the PIs' complementary backgrounds. We now briefly describe
these backgrounds.

@@

Irregular applications are increasing in importance to the computing industry.  For a long time they have underpinned computations of interest to the national security arm of the federal government.  But now, they underpin such questions as ad placement in social networks, and analysis of complex data-sets in medicine and science.  The defining characteristic of these applications is poor locality and massive available parallelism.  Our effort is focused on making these applications perform well and scale on commodity hardware.  The ``secret sauce'' that makes this work is to essentially build a software XMT~\cite{xmt}.  Instead of relying on locality (which doesn't exist for these applications) we rely on threading to tolerate memory latency.  Unlike the XMT, however, we must contend with commodity networking hardware, and here we again rely on threading to provide a sufficient number of requests that we can buffer them prior to dispatching on the physical wire.

>>>>

PI Oskin has traditionally participated in the computer-architecture research
community, co-PI Ceze, in addition to the architecture community also has a
presence in the systems and programming languages community, and co-PI Kahan
has participated mainly in the parallel and scientific computing community.
The move toward multicore architectures has re-invigorated collaboration
across these divides and recent joint work by Oskin, Ceze, and Kahan
embodies this important trend. There are currently five graduate students for
which last two of the PIs serve as advisors. In addition to the project
described in this proposal, they are working together on techniques for
detecting concurrency errors with machine learning and language
specifications, using disciplined approximations to save energy in computing,
and developing new operating-system abstractions for emerging non-volatile
memory devices. What has made these collaborations so fruitful in such a short
period of time is the PIs' complementary backgrounds. We now briefly describe
these backgrounds.

@@

Irregular applications are increasing in importance to the computing industry.  For a long time they have underpinned computations of interest to the national security arm of the federal government.  But now, they underpin such questions as ad placement in social networks, and analysis of complex data-sets in medicine and science.  The defining characteristic of these applications is poor locality and massive available parallelism.  Our effort is focused on making these applications perform well and scale on commodity hardware.  The ``secret sauce'' that makes this work is to essentially build a software XMT~\cite{feo:xmt}.  Instead of relying on locality (which doesn't exist for these applications) we rely on threading to tolerate memory latency.  Unlike the XMT, however, we must contend with commodity networking hardware, and here we again rely on threading to provide a sufficient number of requests that we can buffer them prior to dispatching on the physical wire.
